\documentclass[11pt]{article}
\usepackage[vmargin=1cm,hmargin=3.6cm]{geometry}
\usepackage{paralist}
\usepackage{changepage}
\usepackage{DejaVuSerif}
\usepackage[T1]{fontenc}
\begin{document}
\newpage
\newcommand{\myspace}{\vspace{1em}}
\centering
\section*{Agile Manifesto}
\begin{adjustwidth}{1.2cm}{1.2cm}
\centering
We are uncovering better ways of developing software by doing it and helping others do it. Through this work we have come to value:
\myspace

\textbf{Individuals and interactions} over \textit{processes and tools}
\myspace

\textbf{Working software} over \textit{comprehensive documentation}
\myspace

\textbf{Customer collaboration} over \textit{contract negotiation}
\myspace

\textbf{Responding to change} over \textit{following a plan}
\myspace

That is, while there is value in the items on the right, we value the items on the left more.
\end{adjustwidth}
\centering
\section*{Principles}
    % \begin{enumerate}[1.]
     Our highest priority is to satisfy the customer through early and continuous delivery of valuable software.

    \myspace
     Welcome changing requirements, even late in development. Agile processes harness change for the customer's competitive advantage.

    \myspace
     Deliver working software frequently, from a couple of weeks to a couple of months, with a preference to the shorter timescale.

    \myspace
     Business people and developers must work together daily throughout the project.

    \myspace
     Build projects around motivated individuals. Give them the environment and support they need, and trust them to get the job done.

    \myspace
     The most efficient and effective method of conveying information to and within a development team is face-to-face conversation.

    \myspace
     Working software is the primary measure of progress.

    \myspace
     Agile processes promote sustainable development. The sponsors, developers, and users should be able to maintain a constant pace indefinitely.

    \myspace
     Continuous attention to technical excellence and good design enhances agility.

    \myspace
     Simplicity --- the art of maximizing the amount of work \underline{not} done --- is essential.

    \myspace
     The best architectures, requirements, and designs emerge from self-organizing teams.

    \myspace
     At regular intervals, the team reflects on how to become more effective, then tunes and adjusts its behavior accordingly.
    % \end{enumerate}
\end{document}
